Translation of B Implementations to the LLVM: Control and Modularity

### 2013-08-23 translation.tex
Updated the python encoding of example-01 with all the operations. Updated the translation to handle all of example_01, and verified that it is compilable by llvm-as, and that the interpretation with lli behaves as expected. Small changes in the textual description of the translation.

The LLVM tools that are employed are:
\begin{description}
\item[llvm-as] The LLVM assembler generates LLVM bitcode, invoked, e.g., as
  follows:
\begin{verbatim}
llvm-as-mp-3.1 example-01.llvm -o example-01.bc
\end{verbatim}
\item[lli] The LLVM bitcode interpreter, which may be invoked as follows:
\begin{verbatim}
lli-mp-3.1 example-01.bc
\end{verbatim}
\end{description}
\section{Conclusion and future work}
\label{sec:conclusion}

>>>>

The LLVM tools that are employed are:
\begin{description}
\item[llvm-as] The LLVM assembler generates LLVM bitcode, invoked, e.g., as
  follows:
\begin{verbatim}
llvm-as-mp-3.1 example-01.llvm -o example-01.bc
\end{verbatim}
\item[lli] The LLVM bitcode interpreter, which may be invoked as follows:
\begin{verbatim}
lli-mp-3.1 example-01.bc
\end{verbatim}
\end{description}

Once a rule has been manually validated, we implement it in a prototype tool
written in Python. Unfortunately the tool does not take as input the B0 source
file, but instead a collection of Python definitions corresponding to the
syntactic entities present in the parse tree. For instance, for an integer
concrete variable named \B{value}, we would have the following Python entity:
\begin{verbatim}
value = { "kind": "Vari",
          "id": "value",
          "type": "INT",
          "scope": "impl",
          "root": counter_i}
\end{verbatim}
where \verb'counter_i' would be the Python entity representing the parse tree
root for the B implementation. Again the output generated by the prototype
is compiled and simulated using off-the-shelf LLVM tools \verb'llvm-as' and
\verb'lli'.

\section{Conclusion and future work}
\label{sec:conclusion}
